Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-04-02 analysis/paper/paper.Rmd
working on fig 2

paramTableDem = paramTable
paramTableDem$weightFunction = deparse1(slopePenaltyFn,collapse="\n")
paramTableDem$weightFunction = gsub("limitWeight = NA","limitWeight = 65000",paramTableDem$weightFunction,fixed=T)

# re-run projections for just the small area with different parameters
mstProj <- projectAll(tsbs = tsb, paramTable = paramTable,
                      weightRaster = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"),
                      roadsInWeight = F)

ilcpProj <- projectAll(tsbs = tsb,
                      paramTable = paramTable %>% 
                        filter(sampleType == "regular") %>% 
                        mutate(method = "ilcp"),
                      weightRaster = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"),
                      roadsInWeight = F)

# re-run projections for just the small area with different parameters
mstProjDem <- projectAll(tsbs = tsb, paramTable = paramTableDem,
                      weightRaster = dem,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"),
                      roadsInWeight = F)

ilcpProjDem <- projectAll(tsbs = tsb,
                      paramTable = paramTableDem %>% 
                        filter(sampleType == "regular") %>% 
                        mutate(method = "ilcp"),
                      weightRaster = dem,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"),
                      roadsInWeight = F)

allProj <- bind_rows(mstProj, ilcpProj, mstProjDem, ilcpDem, .id = "method") %>%
  arrange(desc(sampleType), sampleDens)

@@

allProj <- bind_rows(
  allProj,
  tibble(sampleType = "", sampleDens = 0, method = "Hardy QGIS",
             output = list(here(data_path_drvd, "..", "for_fig", 
                                "HardyQGISTest.gpkg")))) %>% 
  mutate(mapTitle =  paste(ifelse(method == 1, "MST",
                                  ifelse(method == 2, "ILCP", method)),
                           weightMethod,
                           sampleType,
                           ifelse(sampleDens == 1e-06 & 
                                    sampleType != "centroid", "low density", 
                                  ifelse(sampleDens == 1e-05, 
                                         "high density", ""))))

@@

tmap_save(tmap_arrange(allMaps, ncol = 3),
          here("analysis/figures/projection_methods_figure.png"),
          dpi = 300, height = 5, width = fig_widths["two"])
```

>>>>

paramTableDem = paramTable
paramTableDem$weightFunction = deparse1(slopePenaltyFn,collapse="\n")
paramTableDem$weightFunction = gsub("limitWeight = NA","limitWeight = 65000",paramTableDem$weightFunction,fixed=T)
paramTableDem$weightMethod = "grade penalty"

paramTableDem<- subset(paramTableDem,sampleType!="centroid")

# re-run projections for just the small area with different parameters
mstProj <- projectAll(tsbs = tsb, paramTable = paramTable,
                      weightRaster = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd,"..", "for_fig"),
                      roadsInWeight = F)

ilcpProj <- projectAll(tsbs = tsb,
                       paramTable = paramTable %>%
                         filter(sampleType == "regular") %>%
                         mutate(method = "ilcp"),
                       weightRaster = tsaCost,
                       cutblocks = cutblocks,
                       existingRoads = exRoads,
                       fileLocation = here(data_path_drvd,"..", "for_fig"),
                       roadsInWeight = F)

# re-run projections for just the small area with different parameters
mstProjDem <- projectAll(tsbs = tsb, paramTable = paramTableDem,
                         weightRaster = dem,
                         cutblocks = cutblocks,
                         existingRoads = exRoads,
                         fileLocation = here(data_path_drvd,"..", "for_fig"),
                         roadsInWeight = F)

ilcpProjDem <- projectAll(tsbs = tsb,
                          paramTable = paramTableDem %>%
                            filter(sampleType == "regular") %>%
                            mutate(method = "ilcp"),
                          weightRaster = dem,
                          cutblocks = cutblocks,
                          existingRoads = exRoads,
                          fileLocation = here(data_path_drvd,"..", "for_fig"),
                          roadsInWeight = F)

allProj <- bind_rows(mstProj, ilcpProj, mstProjDem, ilcpProjDem) %>%
  arrange(weightMethod,desc(sampleType), sampleDens)

@@

allProj <- bind_rows(
  allProj,
  tibble(sampleType = "", sampleDens = 0, method = "Hardy QGIS",
         output = list(here(data_path_drvd,"..", "for_fig",
                            "HardyQGISTest.gpkg")))) %>%
  mutate(mapTitle =  paste(weightMethod,
                           ifelse(method == "mst", "MST",
                                  ifelse(method == "ilcp", "ILCP", method)),
                           sampleType,
                           ifelse(sampleDens == 1e-06 &
                                    sampleType != "centroid", "low density",
                                  ifelse(sampleDens == 1e-05,
                                         "high density", ""))))

@@

tmap_save(tmap_arrange(allMaps, ncol = 3),
          here("analysis/figures/projection_methods_figure.png"),
          dpi = 300, height = 8, width = fig_widths["two"])
```
